The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH]

### 2024-02-13 paper/paper.qmd
Progressing in Data and Results.

+ The vast majority of married men in Saudi Arabia privately support WWOH
+ The married men massively underestimate the level of support from other men in their communities
+ Correcting these beliefs about others’ feelings will affect their wives decisions to work.

For this paper, our estimand is the difference between the married men's guess on how many people in their survey group support WWOH and the actual percentage of people in their group that support WWOH.

The remainder of this paper is structured as follows. We will first describe our data sources in @sec-data (Data), followed by a description of the variables and methodologies utilized by the original paper in @sec-results (Results). We will then conduct a reproduction of certain figures and results to verify the original paper’s findings in the same section. Afterwards, we will summarize our results when compared to the original paper. We will additionally conduct an in-depth examination of how various demographics affect the support for WWOH. Lastly, in @sec-discussion (Discussion), we will discuss the findings from @sec-results (Results) in context.

@@

# Results {#sec-results}

@@

summary_all <- wwoh_data |>
  summarize(
    Observations = n(),
    Mean_age = mean(age, na.rm =TRUE),
    Mean_children = mean(children, na.rm = TRUE),
    Percent_college = sum(college_deg, na.rm = TRUE)/n()*100,
    Percent_employed = sum(employed_now, na.rm = TRUE)/n()*100)

@@

Our results are summarized in @tbl-modelresults.

>>>>

+ The vast majority of married men in Saudi Arabia privately support WWOH
+ The married men massively underestimate the level of support from other men in their communities
+ Correcting these beliefs about others’ feelings will affect the outcome of whether the married man's wife work.

For this paper, our estimand is the difference between the married men's guess on how many people in their survey group support WWOH and the actual percentage of people in their group that support WWOH. The remainder of this paper is structured as follows. We will first describe our data sources in @sec-data (Data), followed by a description of the variables and methodologies utilized by the original paper in @sec-results (Results). We will then conduct a reproduction of certain figures and results to verify the original paper’s findings in the same section. Afterwards, we will summarize our results when compared to the original paper. We will additionally conduct an in-depth examination of how various demographics affect the support for WWOH. Lastly, in @sec-discussion (Discussion), we will discuss the findings from @sec-results (Results) in context.

@@

## Data source and collection
The data used in this analysis - Main Experiment of Saudi Arabia men on WWOH and their beliefs of others’ opinions  - is sourced from the replication package provided by Bursztyn et.al (year). The data was collected by the researchers in the original paper through an experiment and repeated surveys with a treatment group and a control group. This analysis will be carried out in R [6] using packages tidyverse [7], knitr [8], dplyr [9], ggplot2 [10], knitr [8], and here [11]. Although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis. The paper was published in the American Economic Review 2020, 110(10) issue between pages 2997-3029 (). The data was similarly uploaded at the same time and has not been updated since.

More specifically, the sampling for the experiment was conducted through a partnership between a local branch of an international survey company and Bursztyn et.al. They recruited 500 Saudi Arabia men between the ages of 18 and 35, living across Riyadh, Saudi Arabia ().

# Results {#sec-results}
In this section, we will replicate some of the graphs, tables, and findings in the original paper.

The data collected from the experiment can be introduced through summary statistics.

@@

summary_all <- wwoh_data |>
  summarize(
    Observations = n(),
    Age = mean(age, na.rm =TRUE),
    Children = mean(children, na.rm = TRUE),
    "College" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100)

@@

As seen in @tbl-sum above, there are less than 500 data points present after removing single men as well as any empty data points used in the making of the summary statistics, contrary to the claims of Bursztyn et.al.
